---
title: "Cabbages"
author: "Ashley Davis"
date: "Summer 2023"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  

$H_0$: No difference in vitamin C content of cabbages based on the cultivation technique

$H_A$: There is a difference in the vitamin c content of cabbages based on cultivation technique

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

The response variable(how much vitamin c) is numerical; the input variable is categorical. We have a Num ~ Cat.

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(VitC~Cult,data=veggy)
```

This table shows the cultivation method c52 has a higher vitamin C content than does c39. C52 shows an average difference of about 13 mg.

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
plot(VitC~Cult,data=veggy)
```

This graph shows that cultivation method c52 contains a higher vitamin c level in the cabbages than cultivation method c39.

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfies the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(VitC~Cult,data=veggy)
```
The P-value = 0.00000003405, is so small that I must reject $H_0$ and conclude that there is a difference between the cultivation methods. 

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variables causes the other, or whether they perhaps are related for some other reason.  Watch the chapter 6 videos from the George Town videos collection.!-->

The original question posed was whether there was a difference in vitamin C content based on the cultivation methods c52 and C39. 

Based on the T=Test, we found that cultivation method c52 has demonstrated a higher vitamin C content in the cabbages than c39.

Therefore, I must recommend cultivation method c52 for harvesting cabbages with a higher vitamin C content.
